### 2019-02-27 papers/journal/prelim.tex
Small fix

\subsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC/SMT/QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning(CDCL)~\cite{cdcl}.
%
The QBF solver add support of quantifiers by adding more rules for
quantifiers~\cite{qbf}.

>>>>

\subsection{Solvers}
In this paper, we will encode several problems into finding satisfying
solutions of a Boolean formula or QBFs.
%
We will use BMC,SMT and QBF solvers to get the satisfying assignments.
%
The modern solvers are result of several decades of research
and implement sophisticated algorithms.
%
A SAT solver typically implements conflict-driven clause learning (CDCL)~\cite{cdcl}.
%
The QBF solver add support of quantifiers by adding more rules for
quantifiers~\cite{qbf}.
